### 2018-06-27 Sections/optimising_the_world.tex
Complexity classes fig
Graph colouring

@@

Note that for the quantum search method for enhancing \textbf{NP}-complete problems, a quadratic improvement is optimal. Therefore, \mbox{$p\leq 2$}.

>>>>

\subsubsection{Graph colouring}\index{Graph colouring}

One particularly useful approach to representing various optimisation problems is to relate them to the \textit{graph colouring problem}. This problem is known to be \textbf{NP}-complete, and when operating on a graph with $n$ vertices has $O(2^nn)$ classical runtime using the best known algorithm.

The goal of the graph colouring problem is to take a graph $G$, and a set of $k$ colours, and assign a colour to each vertex such that no two vertices connected via an edge share the same colour. If such an assignment of colouring exists, we say the graph is $k$-colourable. The \textit{chromatic number}\index{Chromatic number} of $G$, denoted \mbox{$\chi(G)$}, is the smallest number $k$ such that the graph is $k$-colourable. An example is shown in Fig.~\ref{fig:graph_colouring}.

\begin{figure}[!htb]
\includegraphics[width=0.3\textwidth]{graph_colouring}
\caption{Example of a graph with 3-colouring, such that no two vertices connected by an edge share the same colour. For this particular graph, 3-colouring is optimal (in the sense that the number of colours in minimised). It can easily be seen upon inspection that no 2-colouring is possible for this graph. Thus, this graph's chromatic number is \mbox{$\chi(G)=3$}\index{Chromatic number}.}\index{Graph colouring}\label{fig:graph_colouring}	
\end{figure}

This problem relates closely to the \textit{map colouring problem}\index{Map colouring}, where the goal is to assign colours to states within a map, such that no two neighbouring states share the same colour. The map colouring problem is a subset of the graph colouring problem.

How does this problem relate to optimisation? Here are two simple examples demonstrating the usefulness of the graph colouring problem in optimisation theory.

\paragraph{Constrained time-scheduling}\index{Constrained time-scheduling}

Our goal is to schedule the execution of a large number of tasks, so as to minimise total execution time. However, some tasks may conflict with others -- for example, they compete for access to a shared resource, which can only serve one task at a time.

Let the vertices in the graph represent tasks, and let colours represent distinct points in time. If two tasks are in competition with one another and cannot be executed simultaneously, we designate an edge between them. Thus, the set of edges in this `conflict graph'\index{Conflict graph} fully characterises all conflicts in resource allocation between tasks.

Now finding a valid scheduling of tasks amounts to solving the graph colouring problem on the conflict graph, where the colouring specifies the temporal order in which tasks ought to be executed. The graph's chromatic number, $\chi(G)$, now tells us the minimum time in which all tasks can be executed subject to their constraints.

\paragraph{Broadcast networks}\index{Broadcast networks}

Consider a country comprising different regions, where each region is served by its own local radio station. But the radio signal within a region is strong enough to penetrate its immediate neighbouring regions also. For this reason, the frequency at which a regional station transmits should never be the same as that of its neighbours, so as to avoid signal interference.

In this version of the map colouring problem, a valid colouring specifies a set of transmission frequencies that avoid interregional interference, and the chromatic number specifies the smallest possible radio spectrum that must be allocated to the stations\footnote{Spectrum is worth a lot of money!}.

The same principles could apply to all manner of broadcast networks, such as the allocation of spectrum in cellular phone networks\index{Cellular phone networks}.

@@

Note that for the quantum search method for enhancing \textbf{NP}-complete problems, a quadratic improvement is known to be optimal. Therefore, \mbox{$p\leq 2$}.
